\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-09-05 paper/ms.tex
Version bump

The \proglang{Python}
packages \pkg{NumPy} \citep{numpy}, \pkg{matplotlib} \citep{matplotlib},
and \pkg{Cython} \citep{cython} are also needed.
To download and compile \pkg{DNest4}
the following steps are sufficient:
\begin{CodeChunk}
\begin{CodeInput}
> wget https://github.com/eggplantbren/DNest4/archive/0.1.2.tar.gz
> tar xvzf 0.1.2.tar.gz
> mv DNest4-0.1.2 DNest4
> cd DNest4/code
> make
> cd ../python
> python setup.py install
\end{CodeInput}
\end{CodeChunk}

>>>>

The \proglang{Python}
packages \pkg{NumPy} \citep{numpy}, \pkg{matplotlib} \citep{matplotlib},
and \pkg{Cython} \citep{cython} are also needed.
To download and compile \pkg{DNest4}
the following steps are sufficient:
\begin{CodeChunk}
\begin{CodeInput}
> wget https://github.com/eggplantbren/DNest4/archive/0.1.3.tar.gz
> tar xvzf 0.1.3.tar.gz
> mv DNest4-0.1.3 DNest4
> cd DNest4/code
> make
> cd ../python
> python setup.py install
\end{CodeInput}
\end{CodeChunk}
